Macro Impacts

### 2016-08-03 Macro Impacts Revised.tex
correction

The approximation (32) holds when $bk_0\ll 1$, and is always an overestimate. Since we know $b$ is on the order of meters, this is, in fact, a good approximation. Thus

@@

$A$ is a constant which characterizes the explosion for small $k$. In the case that $f$ is constant, $A = 1$.

>>>>

The approximation (32) holds when $bk_0\ll 1$, and is always an overestimate. Since we know $b$ is on the order of meters, this is, in fact, a good approximation ($k_0$ is of order millimeters). Thus

@@

$A$ is a constant which characterizes the explosion for small $k$. In the case that $f$ is constant, $A = f\times (b^2-a^2)$. If $f$ is the triangle from section 2, then $A = \f16\Delta r(3r_0 + 2\Delta r)$.
